### 2022-03-14 scratch.rmd
added faceted graph with a few ideas

```{r}
library(gssr)
library(tidyverse)
# don't recommend getting single year -- not enough data
# gss21 <- gss_get_yr(2021)
# gss21["sexsex"]
data(gss_all)

```
```{r}
gss_clean <- gss_all |>
  mutate(
    id = paste0(year, '_', id),
    sexnow = coalesce(sexnow, sexnow1),
    sexbirth = coalesce(sexbirth, sexbirth1)
    ) |>
  select(-sexnow1, -sexbirth1)
```

@@

>>>>

```{r}
library(gssr)
library(tidyverse)
# don't recommend getting single year -- not enough data
# gss21 <- gss_get_yr(2021)
# gss21["sexsex"]

```

```{r}
data(gss_all)
```

```{r}
gss_clean <- gss_all |>
  mutate(
    id = paste0(year, '_', id),
    sexnow = coalesce(sexnow, sexnow1) |> as_factor(),
    sexbirth = coalesce(sexbirth, sexbirth1) |> as_factor(),
    sexornt = as_factor(sexornt),
    sexsex = as_factor(sexsex),
    sexsex5 = as_factor(sexsex5)
    ) |>
  select(id, sexnow, sexbirth, sexornt, sexsex, sexsex5)
```
```{r}

```

@@

```{r}
gss_clean |>
  filter(!if_any(c(sexsex, sexnow, sexornt), is.na)) |>
  ggplot(aes(x = sexsex, fill=sexsex)) +
  geom_histogram(stat="count") +
  scale_fill_manual(values=c('blue', 'purple', 'red')) +
  theme(axis.text.x = element_blank()) +
  facet_grid(sexnow ~ sexornt,
             scales = "free_y")
```
```{r}
gss_clean |>
  filter(!if_any(c(sexsex5, sexnow, sexornt), is.na)) |>
  ggplot(aes(x = sexsex5, fill=sexsex5)) +
  geom_histogram(stat="count") +
  scale_fill_manual(values=c('blue', 'purple', 'red')) +
  #geom_text(stat="count", aes(label=..count..), position = position_stack(vjust=.5), color="black") +
  theme_bw() + 
  theme(
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    panel.grid.major.x = element_blank()
    ) +
  facet_grid(sexornt ~ sexnow,
             scales = "free_y",
             labeller = label_wrap_gen(width = 16, multi_line = T)
             )
```
